---
title: Portfolios
author: 'Travis Gerke'
date: '2022-07-27'
slug: ["portfolios"]
categories: ["portfolios"]
tags: ["websites", "github"]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Portfolios

The [WTF AITA talk](https://wtf-aita.com/talk/#/portfolios) highlighted 3 ways to create a quick portfolio for yourself.

## Make a GitHub profile

Here's a helpful [walkthrough using the GitHub UI](https://aboutmonica.com/blog/how-to-create-a-github-profile-readme/) from Monica Powell. If, instead, you want to jumpstart this with 3 lines of R code, here you go!

```{r eval=FALSE}
# Make a project that is titled your GitHub user name
usethis::create_project("~/Documents/GHusername")

# Connect it to GitHub
usethis::use_github()

# Once in the project, run this to make your readme
usethis::use_readme_rmd()
```

Knit your changes to the basic template and you're good to go!

## Make a personal landing page

The example in the talk ([Hadley Wickham's page](https://hadley.nz/)) uses the [postcards](https://github.com/seankross/postcards) package. Check the excellent vignette at the package site to quickly get started.

## Make a website/blog

This is the more advanced option, but there are many great design choices and tools to help you!

- Alison Hill's [site](https://www.apreshill.com/) made with Hugo Apero and a corresponding [walkthrough](https://www.apreshill.com/talk/2021-iyo-tunis/) for getting started
- Danielle Navarro's [site](https://blog.djnavarro.net/) ported from distill to quarto, with corresponding [walkthrough](https://blog.djnavarro.net/posts/2022-04-20_porting-to-quarto/)
